Constraining gravitational wave amplitude birefringence with GWTC-3

### 2023-08-28 src/tex/ms.tex
Will's minor edits to Zhu+ discussion.

@@

In \ref{fig:posterior_MPV}, we show the posterior on $M_{\rm PV}^{-1}$ for each event in our analysis.
Compared to Fig.~1 in \citet{Zhu:2023wci}, we can see that the posteriors on some events are different between our analysis and theirs.
For example, the posterior for GW190727\_060333 peaks at zero in our analysis, but peaks at a nonzero value in \citet{Zhu:2023wci}.
This shows that the difference in the combined constraint may come from the difference in the individual event analyses.
However, we could not compare the analysis in \citet{Zhu:2023wci} with ours in detail, as their analysis result is not publicly available.

>>>>

\definechangesauthor[name=Will, color=cyan]{WF}

@@

In \ref{fig:posterior_MPV}, we show the posterior on $M_{\rm PV}^{-1}$ for each event in our analysis.
Compared to Fig.~1 in \citet{Zhu:2023wci}, we can see that the posteriors on some events are different \added[id=WF]{in both scale and shape} between our analysis and theirs.
For example, the posterior for GW190727\_060333 peaks at zero in our analysis, but peaks at a nonzero value in \citet{Zhu:2023wci}.
This shows that the difference in the combined constraint may come from the difference in the individual event analyses.
However, we could not compare the analysis in \citet{Zhu:2023wci} with ours in detail, as their analysis result is not publicly available.
